---
  title: "Assignment 1"
author: "Lily"
date: "`r Sys.Date()`"
output: github_document
always_allow_html: true
---
  
```{r install-libraries}
library(lubridate)
library(tidyverse)
library(data.table)
library(data.table)
library(dtplyr)
library(dplyr)
library(leaflet)
library(ggplot2)
```

# Step 1
```{r Read in Data}
D04 <- data.table::fread("ad_viz_plotval_data.csv")
D19 <- data.table::fread("ad_viz_plotval_data2.csv")
```
### Check dimensions, headers, footers, variable names and variable types
```{r Checks}
dim(D04)
head(D04)
tail(D04)
str(D04)
dim(D19)
head(D19)
tail(D19)
str(D19)
```
### Summary
After checking all the requested aspects of the data, I observed no data issues. 2004 has 20 variables and 19,233 observation while 2019 also has 20 variables with 53,156 observations. 

# Step 2
```{r Merge Data}
DM <- rbind(D04, D19)
```
### Column for Year
```{r Rename}
DM <- mutate(DM, year = factor(rep(c(2004, 2019), c(nrow(D04), nrow(D19))))) %>%
  rename(lat = SITE_LATITUDE, lon = SITE_LONGITUDE)
```

# Step 3
```{r Locations and Year}
DM2 <- DM
DM2 = DM2%>% select(lat, lon, year)
```
### Color Scheme 
```{r Colors}
DMC <- colorFactor("RdYlBu", domain=DM2$year)
DMC
```
### Leaflet
```{r Map}
LDM <- leaflet(DM2)
LDM
```

### Summary 
I observed densely populated site zone in CA. 

# Step 4
```{r missing or implaus}
summary(DM$DM)
```
### Summary 
I did not observe any missing Data

#5 
```{r State}
DM$yday <- yday(DM$Date)
state <- DM2 %>%
  group_by(yday,year) %>%
  summarise(ADM=mean(DM))
```
### Summary State 
We saw lower levels in 2019
```{r county}
DM$yday <- yday(DM$Date)
county <- DM2 %>%
  group_by(yday,year) %>%
  summarise(ADM=mean(DM))
```
### Summary State 
The levels decresed from 2004 to 2019
```{r site}
DM$yday <- yday(DM$Date)
site <- DM2 %>%
  group_by(yday,year) %>%
  summarise(ADM=mean(DM))
```
### Summary State   
We saw new sites appear   
